---
title: "151024 strings_and_factors"
output: github_document
date: "2024-10-15"
---

```{r setup, include=FALSE}
library(rvest)
library(p8105.datasets)
library(tidyverse)
```

# Let's do strings 

Rather than creating dataframe, just create vectors (for now just understanding strings at a small scale), then see how it functions in tidyverse later

Here saying that vector is just 4 words, and try to find specific matches inside. 
Asking for string variable that im looking in a 

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "a")
```

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "Jeff")
```

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, " jeff")
```

See how the detect is very very specific 

Can also replace 

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, " jeff")

str_replace(string_vec, "e", "E")
```

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "i think")
```

since they all have i think, but want to find i think that starts with i think 
```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "^i think")
```

^ indicates beginning of a line

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "i think$")
```

$ indicates end of the line

```{r}
string_vec = c(
  "Time for a Pumpkin Spice Latte!",
  "went to the #pumpkinpatch last weekend",
  "Pumpkin Pie is obviously the best pie",
  "SMASHING PUMPKINS -- LIVE IN CONCERT!!"
  )

str_detect(string_vec,"[Pp]umpkin")

```

Allow for two different options for what we are looking for 

Looking for a pattern here: a number followed by two letters -->

```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "[0-9]")
str_detect(string_vec, "[0-4]")
str_detect(string_vec, "[0-9][a-z]")
str_detect(string_vec, "[0-9][a-zA-Z]")
```

We want to detect 7 followed by any character then 11 
The character . matches anything.

```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```

Not the one in the middle since there is no character seperating the 7 and 11 
Suppose we are looking for a bracket which is usually used as special characters, have special seperate meaning in regular expression 

str_detect(string_vec, "[") <-- this will give 

Put twp backslashs before the special character

```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")

```

